A new machine-learning based prediction of survival in patients with end-stage liver disease

### 2022-08-09 analysis/article.Rmd
refactor: add TB's COI

The authors state no conflict of interest.

>>>>

TB recieved grants or research support from
Abbvie, BMS, Gilead, MSD/Merck, Humedics, Intercept, Merz, Norgine, Novartis, Orphalan, Sequana Medical.
TB received honoraria or consultation fees/advisory board from
Abbvie, Alexion, Bayer, Gilead, GSK, Eisai, Enyo Pharma, Falk Foundation, HepaRegeniX GmbH, Humedics,  Intercept, Ipsen, Janssen, MSD/Merck, Novartis, Orphalan, Roche,
Sequana Medical, SIRTEX, SOBI, and Shionogi
TB participated in a company sponsored speaker’s bureau for
Abbvie, Alexion, Bayer, Gilead, Eisai, Intercept, Ipsen, Janssen, MedUpdate GmbH, MSD/Merck, Novartis, Orphalan, Sequana Medica, SIRTEX, and SOBI.
All other authors state no conflict of interest.
